\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-14 paper/main.tex
fixed the usage of the word environment

\textbf{Bugs.}~We focused on bug reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the bugs have appropriate labels and have been fixed with pull
requests linked to them. Among these confirmed bug reports, we choose
the ones that have enough information to reproduce the bugs, i.e.,
code to reproduce the bug, enviroment required for
reproduction\Fix{Abid, can you confirm that environment here is not
  the same as venv-docker that we are using on Table 1? instead it
  means the version of CUDA, libraries, etc.? If so, avoid (re)using the
  word environment.}, clear description of the desired behavior,
etc. Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset.

>>>>

\textbf{Bugs.}~We focused on bug reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the bugs have appropriate labels and have been fixed with pull
requests linked to them. Among these confirmed bug reports, we choose
the ones that have enough information to reproduce the bugs, i.e.,
code to reproduce the bug, dependencies required for the bug
reproduction
% \Fix{Abid, can you confirm that environment here is not
%   the same as venv-docker that we are using on Table 1? instead it
%   means the version of CUDA, libraries, etc.? If so, avoid (re)using the
%   word environment.}
, clear description of the desired behavior,
etc. Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset.
